DMRGenie: Graphical interface for entanglement renormalization

### 2025-01-09 paper/paper.tex
Update paper.tex
fixes to DMRGenie JS packages and changed TensEZ to DMRGenie

\section{Graphical interface with DMRGenie}
The DMRGenie graphical user interface (GUI) allows for tensor network algorithms to be run with minimal to no coding required, and using diagrams which are easier to read. DMRGenie consists of the Algorithm Runner and the Tensor Network Builder. The Algorithm Runner executes tensor network algorithms such as DMRG using known models or custom Hamiltonians. The Tensor Network Builder allows the user to build their own tensor network and create their own tensor network algorithm using a drag-and-drop system. The frontend was built using HTML, JavaScript, React, and CSS for styling. The backend uses a Model View Controller (MVC) infrastructure. The packages used to run the tensor network algorithms are DMRjulia and TENPACK. So, while both DMRjulia and TENPACK are 100\% from-scratch Julia implementations, DMRGenie is not, but this makes the code easier to use and work with and adapt to changing software standards in the future.

@@

Navigate to the `tensez` directory once the repository has been cloned and then into the `TensEZ` folder within it.

@@

The app must be activated by running the following from the `TensEZ` directory

@@

%Make sure that the path ends with `tensez/TensEZ`, if not then run `{\tt cd("<path\_to\_repo>/tensez/TensEZ")}` from the Julia CLI.
%
%Then exit the Pkg prompt with *backspace*.
%
%Run the following commands
%
%\begin{lstlisting}[language = Julia]
%julia> using Genie
%julia> Genie.loadapp()
%\end{lstlisting}

>>>>

\section{Graphical interface with DMRGenie}
The DMRGenie graphical user interface (GUI) allows for tensor network algorithms to be run with minimal to no coding required, and using diagrams which are easier to read. DMRGenie consists of the Algorithm Runner and the Tensor Network Builder. The Algorithm Runner executes tensor network algorithms such as the density matrix renormalization group (DMRG) using known models or custom Hamiltonians \cite{dmrjulia1}. The Tensor Network Builder allows the user to build their own tensor network and create their own tensor network algorithm using a drag-and-drop system. The frontend was built using HTML, JavaScript, React, and CSS for styling. The backend uses a Model View Controller (MVC) infrastructure. The packages used to run the tensor network algorithms are DMRjulia and TENPACK. So, while both DMRjulia and TENPACK are 100\% from-scratch Julia implementations, DMRGenie is not, but this makes the code easier to use and work with and adapt to changing software standards in the future.

@@

Navigate to the `tensez` directory once the repository has been cloned and then into the `DMRGenie` folder within it.

@@

The app must be activated by running the following from the `DMRGenie` directory

@@

%Make sure that the path ends with `tensez/DMRGenie`, if not then run `{\tt cd("<path\_to\_repo>/tensez/DMRGenie")}` from the Julia CLI.
%
%Then exit the Pkg prompt with *backspace*.
%
%Run the following commands
%
%\begin{lstlisting}[language = Julia]
%julia> using Genie
%julia> Genie.loadapp()
%\end{lstlisting}
